Radio Emission from Red-Giant Hot Jupiters

### 2015-09-27 ms.tex
typo: other the other

% HERA
The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) is a telescope array under construction
in South Africa that will ultimately consist of 352 14-m parabolic dishes, operating from 50 to 250~MHz \citep{pober_et_al2014}.
Unlike other the other telescope observatories considered here, HERA is a dedicated experiment for making power spectral measurements 
of cosmic reionization over wide fields of view.  Similar to its progenitor, the Precision Array to Probe the Epoch of Reionization
(PAPER; \citealt{parsons_et_al2010}), HERA's dishes are deployed in an extremely compact configuration \citep{parsons_et_al2012} and 
statically point toward zenith.  While these features make HERA less ideal for targeted observations, HERA's substantial collecting area,
long observing campaigns, and wide field of view make it a powerful survey instrument.

>>>>

% HERA
The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) is a telescope array under construction
in South Africa that will ultimately consist of 352 14-m parabolic dishes, operating from 50 to 250~MHz \citep{pober_et_al2014}.
Unlike the other telescope observatories considered here, HERA is a dedicated experiment for making power spectral measurements 
of cosmic reionization over wide fields of view.  Similar to its progenitor, the Precision Array to Probe the Epoch of Reionization
(PAPER; \citealt{parsons_et_al2010}), HERA's dishes are deployed in an extremely compact configuration \citep{parsons_et_al2012} and 
statically point toward zenith.  While these features make HERA less ideal for targeted observations, HERA's substantial collecting area,
long observing campaigns, and wide field of view make it a powerful survey instrument.
